# STA 108 HW 1

## 1.2
$y = 2x + 300$ <br>
This is a functional relation because there is no randomness involved. At x visits, we know 100% what y would be.

## 1.8
Yes, E{Y} will still be 104 because the expected value is calculated over many observations, not on one observation. No, the Y value does not have to be 108, because the sampling is random. ??

## 1.12
Observational data, because we are observing two variables to determine if there is a correlation. We observed time spent in exercise and frequency of colds and found a negative correlation.

## 1.27
See appendix for R code.

a. My plot supports that musscle mass decreases as age increases because the regression line has a negative slope.
b.
    1. The slope ($\beta_1 = -1.19$) is the point estimate of difference in mean muscle mass for women differing in age by one year.
    2. $\bar{y}_{x=60} = 79.67$
    3. ??
    4. $s^2 = 262.74$

## 1.30
The implication is that the dependent variable is not affected by the independent variable. The regression function would be a horizontal line on a graph with a y-intercept of $\beta_0$.

# Appendix
## 1.27(a)
```{r}
file_path <- "CH01PR27.txt"
data <- read.table(file_path)
y <- data$V1
x <- data$V2

model <- lm(y ~ x, data = data)
intercept <- coef(model)[1]
slope <- coef(model)[2]
cat("y = ", round(intercept, 2), " + ", round(slope, 2), "x\n", sep = "")

plot(x, y, xlab = "age", ylab = "musscle mass")
abline(model)
```

## 1.27(b)
### 1
```{r}
slope
```

### 2
```{r}
age_60 <- data[x == 60, "V1"]
round(mean(age_60), 2)
```

### 3
??
```{r}

```

### 4
```{r}
round(var(y), 2)
```