# STA 108 HW 1

## 1.2
$y = 2x + 300$ <br>
This is a functional relation because there is no randomness involved. At x visits, we know 100% what y would be.

## 1.8
Yes, E{Y} will still be 104 because the expected value is calculated over many observations, not on one observation. No, the Y value does not have to be 108, because the sampling is random so the error ($\mathcal{E}
_i$) might be different.

## 1.12
a. Observational data, because the predictor variables are uncontrolled and it didn't come from an experimental study.
b. Validity is questionable because it claims a direct causation between number of colds and time exercised, but we only know that there is a correlation.
c. Underlying illness, mobility issues, daily environment.
d. Add more explanatory variables, and make the study a completely randomized experiment.

## 1.27
See appendix for R code.

a. My plot supports that musscle mass decreases as age increases because the regression line has a negative slope.
b.
    1. The slope ($\beta_1 = -1.19$) is the point estimate of difference in mean muscle mass for women differing in age by one year.
    2. $\hat{y}_{x=60} = 84.94683$
    3. $\mathcal{E}_8 = 4.443252$

## 1.30
The implication is that the dependent variable is not affected by the independent variable ($\beta_1 = 0$). The regression function ($y = \beta_0 + \mathcal{E}_i$) would be a horizontal line on a graph with a y-intercept of $\beta_0$.

# Appendix
## 1.27(a)
```{r}
file_path <- "CH01PR27.txt"
data <- read.table(file_path)
y <- data$V1
x <- data$V2

model <- lm(y ~ x, data = data)
intercept <- coef(model)[1]
slope <- coef(model)[2]
cat("y = ", round(intercept, 2), " + ", round(slope, 2), "x\n", sep = "")

plot(x, y, xlab = "age", ylab = "musscle mass")
abline(model)
```

## 1.27(b)
### 1
```{r}
slope
```

### 2
```{r}
new_age <- 60
predict(model, newdata = data.frame(x = new_age))
```

### 3
```{r}
model$residuals[8]
```