```{r echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 1.27-b4
```{r}

# 1.27-b4
file_path <- "CH01PR27.txt"
data <- read.table(file_path)
y <- data$V1
x <- data$V2

model <- lm(y ~ x, data = data)
residual <- residuals(model)
var(residual)
```
$\hat{\sigma}^2 = s^2 = 65.6686$

# 2.6-a ?? hand calculations
```{r}

# 2.6-a
n <- 10
x_i <- c(1, 0, 2, 0, 3, 1, 0, 1, 2, 0)
y_i <- c(16, 9, 17, 12, 22, 13, 8, 15, 19, 11)

x_bar <- mean(x_i)
y_bar <- mean(y_i)

beta_1_hat <- sum((x_i - x_bar) * (y_i - y_bar)) / sum((x_i - x_bar) ** 2)
beta_0_hat <- y_bar - beta_1_hat * x_bar
y_i_hat <- beta_0_hat + beta_1_hat * x_i

mse <- 1 / (n - 2) * sum((y_i - y_i_hat) ** 2)

se_beta_1_hat <- sqrt(mse / sum((x_i - x_bar) ** 2))

critical_t_value <- 2.2621

confidence_lower_bound <- beta_1_hat - critical_t_value * se_beta_1_hat
confidence_upper_bound <- beta_1_hat + critical_t_value * se_beta_1_hat
cat("[", confidence_lower_bound, ", ", confidence_upper_bound, "]", sep = "")
```
The 95% confidence interval for $\beta_1$ is [2.938981, 5.061019]. This means that we are 95% certain that $\beta_1 \in [2.938981, 5.061019]$.

# 2.6-b
```{r}

# 2.6-b
t_s <- (beta_1_hat - 0) / se_beta_1_hat
cat("t =", critical_t_value)
cat("t_s =", t_s)
```
The null hypothesis is that there is no linear relationship ($\beta_1 = 0$). The alternate hypothesis is that there is a linear relationship ($\beta_1 \neq 0$). Since the test statistic ($t_s = 8.528029$) is greater than the critical t-value ($t = 2.2621$), we reject the null hypothesis. Therefore, there is a linear relationship. ?? P-value

# 2.6-c
```{r}

# 2.6-c
se_beta_0_hat <- mse * (1 / n + x_bar ** 2 / sum((x_i - x_bar) ** 2))

confidence_lower_bound <- beta_0_hat - critical_t_value * se_beta_0_hat
confidence_upper_bound <- beta_0_hat + critical_t_value * se_beta_0_hat
cat("[", confidence_lower_bound, ", ", confidence_upper_bound, "]", sep = "")
```
The 95% confidence interval for $\beta_0$ is [9.204676, 11.19532]. This means that we are 95% certain that $\beta_0 \in [9.204676, 11.19532]$.

# 2.6-d
```{r}
t <- 2.2621
t_s <- (beta_0_hat - 9) / se_beta_0_hat
cat("t =", critical_t_value)
cat("t_s =", t_s)
```
The null hypothesis is that the mean number of ampules does not exceed 9.0 ($\beta_0 \leq 9.0$). The alternate hypothesis is that the mean number of ampules does exceed 9.0 ($\beta_0 > 9.0$). Since the test statistic ($t_s = 2.727273$) is greater than the critical t-value ($2.2621$), we reject the null hypotehsis. Therefore, the mean number of ampules does exceed 9.0. ?? P-value

# 2.6-e


# 2.27-a ?? t-test for means, not for correlation
```{r}

# 2.27-a
alpha <- 0.05
df <- 59
result <- t.test(x, y)
cv <- qt(alpha, df)

cat("t =", cv)
cat("t_s =", result$statistic)
cat("p =", result$p.value)
```
$\alpha = 0.05$
<br> The null hypothesis is there is no negative correlation ($\beta_1 \geq 0$). The alternative hypothesis is there is a negative correlation ($\beta_1 < 0$). Using a left tail test where $\alpha = 0.05$ and $\nu = 60 - 1 = 59$, our critical t-value is  $t = -1.671093$. Our test statistic is $t_s = -9.652938$. Since $t_s < t$, we reject the null hypothesis. So we conclude there is a negative correlation. Our p-value is $2.918022 * 10^{-16}$.

# rest ??


# Appendix
```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```