```{r echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 1.27-b4
```{r}

# 1.27-b4
file_path <- "CH01PR27.txt"
data <- read.table(file_path)
y <- data$V1
x <- data$V2

model <- lm(y ~ x, data = data)
residual <- residuals(model)
var(residual)
```
$\hat{\sigma}^2 = s^2 = 65.6686$

# 2.6-a ??! hand calculations
```{r}

# 2.6-a
n <- 10
x_i <- c(1, 0, 2, 0, 3, 1, 0, 1, 2, 0)
y_i <- c(16, 9, 17, 12, 22, 13, 8, 15, 19, 11)

x_bar <- mean(x_i)
y_bar <- mean(y_i)

beta_1_hat <- sum((x_i - x_bar) * (y_i - y_bar)) / sum((x_i - x_bar) ** 2)
beta_0_hat <- y_bar - beta_1_hat * x_bar
y_i_hat <- beta_0_hat + beta_1_hat * x_i

mse <- 1 / (n - 2) * sum((y_i - y_i_hat) ** 2)

se_beta_1_hat <- sqrt(mse / sum((x_i - x_bar) ** 2))

critical_t_value <- 2.2621

confidence_lower_bound <- beta_1_hat - critical_t_value * se_beta_1_hat
confidence_upper_bound <- beta_1_hat + critical_t_value * se_beta_1_hat
cat("[", confidence_lower_bound, ", ", confidence_upper_bound, "]", sep = "")
```
The 95% confidence interval for $\beta_1$ is [2.938981, 5.061019]. This means that we are 95% certain that $\beta_1 \in [2.938981, 5.061019]$.

# 2.6-b
```{r}

# 2.6-b
t_s <- (beta_1_hat - 0) / se_beta_1_hat
cat("t =", critical_t_value)
cat("t_s =", t_s)
```
The null hypothesis is that there is no linear relationship ($\beta_1 = 0$). The alternate hypothesis is that there is a linear relationship ($\beta_1 \neq 0$). Since the test statistic ($t_s = 8.528029$) is greater than the critical t-value ($t = 2.2621$), we reject the null hypothesis. Therefore, there is a linear relationship. The p-value is 0.

# 2.6-c
```{r}

# 2.6-c
se_beta_0_hat <- mse * (1 / n + x_bar ** 2 / sum((x_i - x_bar) ** 2))

confidence_lower_bound <- beta_0_hat - critical_t_value * se_beta_0_hat
confidence_upper_bound <- beta_0_hat + critical_t_value * se_beta_0_hat
cat("[", confidence_lower_bound, ", ", confidence_upper_bound, "]", sep = "")
```
The 95% confidence interval for $\beta_0$ is [9.204676, 11.19532]. This means that we are 95% certain that $\beta_0 \in [9.204676, 11.19532]$.

# 2.6-d
```{r}
t <- 2.2621
t_s <- (beta_0_hat - 9) / se_beta_0_hat
cat("t =", critical_t_value)
cat("t_s =", t_s)
```
The null hypothesis is that the mean number of ampules does not exceed 9.0 ($\beta_0 \leq 9.0$). The alternate hypothesis is that the mean number of ampules does exceed 9.0 ($\beta_0 > 9.0$). Since the test statistic ($t_s = 2.727273$) is greater than the critical t-value ($2.2621$), we reject the null hypotehsis. Therefore, the mean number of ampules does exceed 9.0. Our degrees of freedom is 9. Our p-value is 0.025.

# 2.6-e
??

# 2.27-a ?? t-test for means, not for correlation
```{r}

# 2.27-a
summary_model <- summary(model)
summary_model$coefficients["x", "Pr(>|t|)"]
```
$\alpha = 0.05$
<br> The null hypothesis is there is no negative correlation ($\beta_1 \geq 0$). The alternative hypothesis is there is a negative correlation ($\beta_1 < 0$). Using a left tail test where $\alpha = 0.05$, we reject the null hypotehsis when the p-value is less than alpha ($p < 0.05$), while we fail to reject the null when the p-value is greater than alpha ($\alpha > 0.05$). Our p-value is around 0, so we reject the null hypotehsis. Therefore, we conclude there is a negative correlation.

# 2.27-b
No, because the linear model is too simple to catch all ages, it can only capture the age range in our dataset. Therefore, $\beta_0$ is not a good estimator for early ages. ??

# 2.27-c
```{r}

# 2.27-c
coef <- model$coefficients
b0hat <- coef[1]
b1hat <- coef[2]
mse <- summary_model$sigma ** 2
alpha <- 0.05
p <- 1 - alpha / 2
se_b1hat <- summary_model$coefficients["x", "Std. Error"]
lb_b1hat <- b1hat - qt(p, df = n - 2) * se_b1hat
ub_b1hat <- b1hat + qt(p, df = n - 2) * se_b1hat
cat("Confidence Interval is [", lb_b1hat, ", ", ub_b1hat, "]", sep = "")
```
It is not necessary to know the ages to make the estimate because we are making an overall estimate, not an estimate at a specific age.

# 2.28-a

# Appendix
```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```