```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r Functions}
r_matrix_to_mathjax <- function(mat) {
  nrow <- dim(mat)[1]
  ncol <- dim(mat)[2]

  result <- "\\begin{bmatrix}"
  for (i in 1:nrow) {
    result <- paste(result, "", paste(mat[i, ], collapse = "&"), "\\\\")
  }
  result <- paste(result, "\\end{bmatrix}")

  return(result)
}
```

# 5.1
```{r 5.1}
A <- matrix(c(1, 4, 2, 6, 3, 8), nrow = 3, ncol = 2, byrow = TRUE)
B <- matrix(c(1, 3, 1, 4, 2, 5), nrow = 3, ncol = 2, byrow = TRUE)
C <- matrix(c(3, 8, 1, 5, 4, 0), nrow = 2, ncol = 3, byrow = TRUE)

# r_matrix_to_mathjax(A+B)
# r_matrix_to_mathjax(A-B)
# r_matrix_to_mathjax(A%*%C)
# r_matrix_to_mathjax(A%*%t(B))
# r_matrix_to_mathjax(t(B)%*%A)
```

- $A + B = `r r_matrix_to_mathjax(A+B)`$ is a matrix of $3 \times 2$
- $A - B = `r r_matrix_to_mathjax(A-B)`$ is a matrix of $3 \times 2$
- $AC = `r r_matrix_to_mathjax(A%*%C)`$ is a matrix of $3 \times 3$
- $AB' = `r r_matrix_to_mathjax(A%*%t(B))`$ is a matrix of $3 \times 3$
- $B'A = `r r_matrix_to_mathjax(t(B)%*%A)`$ is a matrix of $2 \times 2$

# 5.3.1
Matrix form: $Y - \hat{Y} = e$

$Y = \begin{bmatrix}Y_1\\Y_2\\Y_3\\Y_4\end{bmatrix}$ is a $4 \times 1$ matrix

$\hat{Y} = \begin{bmatrix}\hat{Y_1}\\\hat{Y_2}\\\hat{Y_3}\\\hat{Y_4}\end{bmatrix}$ is a $4 \times 1$ matrix

$e = \begin{bmatrix}(Y_1 - \hat{Y_1})\\(Y_2 - \hat{Y_2})\\(Y_3 - \hat{Y_3})\\(Y_4 - \hat{Y_4})\end{bmatrix}$ is a $4 \times 1$ matrix

# 5.3.2
Matrix form: $Xe = \begin{bmatrix}X_1 e_1 + X_2 e_2 + X_3 e_3 + X_4 e_4\end{bmatrix} = 0$

$X = \begin{bmatrix}X_1&X_2&X_3&X_4\end{bmatrix}$ is a matrix of $1 \times 4$

$e = \begin{bmatrix}e_1\\e_2\\e_3\\e_4\end{bmatrix}$ is a matrix of $4 \times 1$

# 5.8.a
```{r 5.8}
B <- matrix(c(1, 5, 0, 1, 0, 5, 1, 0, 5), nrow = 3, ncol = 3, byrow = TRUE)
det_B <- det(B)
rank_B <- qr(B)$rank
# pracma::rref(B)
```
$det(B) = `r det_B`$

Since $det(B) = 0$, this is linearly dependent.

# 5.8.b
$rref(B) = `r r_matrix_to_mathjax(pracma::rref(B))`$

$rank(B) = `r rank_B`$

# Appendix
```{r appendix, results="asis"}
# Get all the labels
all_labels <- knitr::all_labels()

# Print out code along with labels
for (label in all_labels) {
  if (label == "setup" || label == "appendix") {
    next
  }

  code <- knitr::knit_code$get(label)

  cat("##", label, "\n")
  cat("```r \n")
  cat(code, sep = "\n")
  cat("```\n")
}
```