```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r Function}
r_matrix_to_mathjax <- function(mat) {
  nrow <- dim(mat)[1]

  result <- "\\begin{bmatrix}"
  for (i in 1:nrow) {
    result <- paste(result, "", paste(mat[i, ], collapse = "&"), "\\\\")
  }
  result <- paste(result, "\\end{bmatrix}")

  return(result)
}
```

# 5.5
```{r 5.5}
x1 <- c(4, 1, 2, 3, 3, 4)
Y <- as.matrix(c(16, 5, 10, 15, 13, 22))
X <- cbind(1, x1)

Xt <- t(X)
Yt <- t(Y)
Yt.Y <- Yt %*% Y
Xt.X <- Xt %*% X
Xt.Y <- Xt %*% Y

H <- round(X %*% solve(Xt %*% X) %*% Xt, 4)
H.2 <- round(H %*% H, 4)
```

$X = `r r_matrix_to_mathjax(X)`$

$Y = `r r_matrix_to_mathjax(Y)`$

$Y'Y = `r r_matrix_to_mathjax(Yt)` `r r_matrix_to_mathjax(Y)` = `r r_matrix_to_mathjax(Yt.Y)`$

$X'X = `r r_matrix_to_mathjax(Xt)` `r r_matrix_to_mathjax(X)` = `r r_matrix_to_mathjax(Xt.X)`$

$X'Y = `r r_matrix_to_mathjax(Xt)` `r r_matrix_to_mathjax(Y)` = `r r_matrix_to_mathjax(Xt.Y)`$

# 5.5 Idempotent Proof
Using R:

$H^2 = `r r_matrix_to_mathjax(H.2)`$

$H = `r r_matrix_to_mathjax(H)`$

$\therefore H^2 = H$

By Hand:

$H ^ 2 = (X(X'X)^{-1}X')(X(X'X)^{-1}X')$

$\to H ^ 2 = (X(X^{-1}X'^{-1})X')(X(X'X)^{-1}X')$

$\to H ^ 2 = (XX^{-1}X'^{-1}X')(X(X'X)^{-1}X')$

$\to H ^ 2 = ((XX^{-1})(X'^{-1}X'))(X(X'X)^{-1}X')$

$\to H ^ 2 = (II)(X(X'X)^{-1}X')$

$\to H ^ 2 = I(X(X'X)^{-1}X')$

$\to H ^ 2 = X(X'X)^{-1}X'$

$\to H ^ 2 = H$

$\therefore$ $H$ is idempotent

# 5.17
$W_1 = \begin{bmatrix} 1 & 1 & 1 \end{bmatrix} Y$

$W_2 = \begin{bmatrix} 1 & -1 & 0 \end{bmatrix} Y$

$W_3 = \begin{bmatrix} 1 & -1 & -1 \end{bmatrix} Y$

$W = \begin{bmatrix} W_1 \\ W_2 \\ W_3 \end{bmatrix} = \begin{bmatrix} Y_1 + Y_2 + Y_3 \\ Y_1 - Y_2 \\ Y_1 - Y_2 - Y_3 \end{bmatrix}$

$E\{W\} = \begin{bmatrix} 
  \mu_1 + \mu_2 + \mu_3 \\
  \mu_1 - \mu_2 \\
  \mu_1 - \mu_2 - \mu_3
  \end{bmatrix}$

# 5.24.a
```{r 5.24}
beta_hat <- solve(Xt.X) %*% Xt %*% Y

Y_hat <- X %*% beta_hat
residuals <- Y - Y_hat

Y_mean <- mean(Y)
SSR <- sum((Y_hat - Y_mean)^2)

SSE <- sum(residuals ** 2)

n <- length(x1)
dfSSE <- n - 2
MSE <- SSE / dfSSE
Var.b <- solve(Xt.X) * as.numeric(MSE)

X1h <- 4
Yh <- beta_hat[1] + beta_hat[2] * X1h

X1h <- 4
x_h <- c(1, X1h)
s2_pred <- MSE * (1 + t(x_h) %*% solve(Xt.X) %*% x_h)
```
1. $\hat \beta = `r r_matrix_to_mathjax(round(beta_hat, 4))`$
2. $e = `r r_matrix_to_mathjax(round(residuals, 4))`$
3. $SSR = `r round(SSR, 4)`$
4. $SSE = `r round(SSE, 4)`$
5. $s^2\{b\} = `r r_matrix_to_mathjax(round(Var.b, 4))`$
6. $E\{Y_h\} = `r round(Yh, 4)`$
7. $s^2\{pred\} = `r round(s2_pred, 4)`$

# 5.24.b
1. $s\{b_0, b_1\} = `r round(Var.b[1, 2], 4)`$
2. $s\{b_0\} = `r round(Var.b[1, 1], 4)`$
3. $s\{b_1\} = `r round(Var.b[2, 2], 4)`$

# 6.1.a
$Y = \beta^T X + \epsilon$

$X = \begin{bmatrix}
  1 & x_{11} & x_{11}x_{12} \\
  1 & x_{21} & x_{21}x_{22} \\
  1 & x_{31} & x_{31}x_{32} \\
  1 & x_{41} & x_{41}x_{42}
  \end{bmatrix}$

$\beta = \begin{bmatrix}
  \beta_0 \\
  \beta_1 \\
  \beta_2
  \end{bmatrix}$

# 6.1.b
$log(Y) = \beta^T X + \epsilon$

$X = \begin{bmatrix}
  1 & x_{11} & x_{12} \\
  1 & x_{21} & x_{22} \\
  1 & x_{31} & x_{32} \\
  1 & x_{41} & x_{42}
  \end{bmatrix}$

$\beta = \begin{bmatrix}
  \beta_0 \\
  \beta_1 \\
  \beta_2
  \end{bmatrix}$

# 6.22.a
This is not a linear regression model. We can apply the following transformations:

$X_{i1}' = X_{i1}$

$X_{i2}' = 10 ^ {X_{i2}}$

$X_{i3}' = X_{i1} ^ 2$

Our linear regression model after the transformation:

$Y_i = \beta_0 + \beta_1 X_{i1}' + \beta_2 X_{i2}' + \beta_3 X_{i3}' + \epsilon_i$

# 6.22.b
This is not a linear regression model. It is not possible to transform this.

# Example 6.9
$b_0:$ The intercept in the linear regression model.

$b_1:$ The slope of $x_1$ in the linear regression model.

$b_2:$ The slope of $x_2$ in the linear regression model.

# Appendix
```{r appendix, results="asis"}
# Get all the labels
all_labels <- knitr::all_labels()

# Print out code along with labels
for (label in all_labels) {
  if (label == "setup" || label == "appendix") {
    next
  }

  code <- knitr::knit_code$get(label)

  cat("```r \n")
  cat("# ", label, "\n", sep = "")
  cat(code, sep = "\n")
  cat("```\n")
}
```