---
title: "Quiz 2"
author: "Andrew Jowe"
---

```{r label="noEcho", echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
# plug in data
x <- c(10, 10, 10, 10, 24, 24, 24, 24, 32, 32, 32, 32, 40, 40, 40, 40)
y <- c(199, 205, 196, 200, 218, 220, 215, 223,
       237, 234, 235, 230, 250, 248, 253, 246)

# find the number of samples
x.n <- length(x)

# find the means
y.b <- mean(y)
x.b <- mean(x)

# find the numerator and denominator for later calculations
n <- sum((x - x.b) * y)
d <- sum((x - x.b) ** 2)

# find the predicted b0 and b1 values
b1 <- n / d
b0 <- y.b - x.b * b1

# find the fitted y value
y_fitted <- b0 + b1 * x

# find the residual
residual <- y - y_fitted

# find the mse
mse <- sum(residual ** 2) / (x.n - 2)

# find the variance of b1
s_squared_b1 <- mse / d

# find the t-statistic of b1
t1 <- b1 / sqrt(s_squared_b1)

# find the p-value of the t-statistic
p <- (1 - pt(t1, x.n - 2, ncp = 0)) * 2

# format a table for nice printing
df <- data.frame(x = x, y = y)
df[["$\\hat y$"]] <- y_fitted
df[["$e_i$"]] <- residual
markdown_table <- knitr::kable(df, format = "markdown")
```

`r markdown_table`

$n = `r x.n`$

$\bar y = `r round(y.b, 4)`$

$\bar x = `r round(x.b, 4)`$

$b_1 = `r round(b1, 4)`$

$b_0 = `r round(b0, 4)`$

$MSE = `r round(mse, 4)`$

$s^2(b_1) = `r round(s_squared_b1, 4)`$

$t_1 = `r round(t1, 4)`$

$p = `r round(p, 4)`$

Given $\alpha = 0.01$ (type I error), the decision rule is that if the $p$ value is smaller than $\alpha$, we reject the null hypothesis. Otherwise, we fail to reject the null hypothesis.

Since $p < \alpha$, we reject the null hypothesis. Therefore, $\beta_1 \neq 0$.

\newpage
# Appendix
```{r ref.label=knitr::all_labels()[!grepl("noEcho", knitr::all_labels())], echo=TRUE, eval=FALSE}
```